Jeff Goldsmith

### 2019-05-13 papers.Rmd
CV update (may 2019)

@@

J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018+). 
Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
<i> Statistics in Biosciences, </i> 
accepted.

@@

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
accepted.
[[Link](https://ieeexplore.ieee.org/document/8424003/)]

>>>>

## 2019

E. A. Gibson, **J. Goldsmith**, and M.-A. Kioumourtzoglou (2019+).
Complex Mixtures, Complex Analyses: an Emphasis on Interpretable Results.
<i> Current Environmental Health Reports, </i> 
accepted.
[[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]

J. Xu, M. Branscheidt, H. Schambra, L. Steiner, M. Widmer, J. Diedrichsen, **J. Goldsmith**, M. Lindquist, T. Kitago, A. R. Luft, J. W. Krakauer, P. A. Celnik, SMARTS Study Group (2019)
Rethinking interhemispheric imbalance as a target for stroke neurorehabilitation.
<i> Annals of neurology, </i> 
<b>85</b> 502-513.
[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1002/ana.25452)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30805956)]

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
<b>66</b> 881-891.
[[Link](https://ieeexplore.ieee.org/document/8424003/)]

R. Liu, R. C. Shelton, N. Eldred-Skemp, **J. Goldsmith**, and S. F. Suglia (2019)
Early Exposure to Cumulative Social Risk and Trajectories of Body Mass Index in Childhood.
<i> Childhood Obesity, </i> 
<b>15</b> 48-55.
[[Link](https://www.liebertpub.com/doi/pdf/10.1089/chi.2018.0116)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30362818)]

@@

J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018). 
Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
<i> Statistics in Biosciences, </i> 
accepted.

@@
